\LARGE \bf The Battle for Filter Supremacy: A Comparative Study of the Multi-State Constraint Kalman Filter and the Sliding Window Filter

### 2015-03-05 Report/project_report.tex
updated conclusion

\subsection{KITTI Dataset}
In addition to the ``Starry Night'' datasets, we also compared the performance of the MSCKF and SWF over four traverses from the KITTI dataset \cite{Geiger:2013:IJRR} totaling $534$ m of urban driving.
We selected these particular traverses because they contained few moving objects, which we found to be common failure cases for both filters.
To accommodate our alternative state parametrization, we used the pre-integrated linear velocity measurements provided in the dataset instead of the raw linear accelerations from the IMU. 
We extracted point features from the left camera in the stereo pair using Speeded Up Robust Features (SURF) \cite{Bay:2008:CVIU} and tracked them temporally using Kanade-Lucas-Tomasi (KLT) tracking \cite{Tomasi:91}.
We rejected outliers using an M-estimator Sample Consensus (MSAC) \cite{TorrZisserman:1998} procedure with a 2-point similarity transform.
% Like the ``Starry Night'' datasets, we initialized 3D points in both filters using the inverse-depth batch optimization of Section \ref{sec:featPosinvDepth}.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \vspace{-0.1cm}
\section{Conclusions} \label{sec:conclusions}
Our results show that both the MSCKF and SWF provide substantial gains in accuracy over pure IMU integration on typical datasets with many visible features.
On the datasets we tested, the SWF slightly outperformed the MSCKF, but the MSCKF improved in accuracy with additional features while the SWF was less sensitive to feature quantity.
It is unclear from these results which algorithm would perform best as the number of features grows very large.

In relatively featureless environments, neither filter performed substantially better than pure IMU integration.
We stress that our inertial data was obtained from high-quality IMUs and has been sanitized to account for gravity, biases, and integration error.
Using a consumer-grade IMU, we expect that pure IMU integration would have performed much worse, and that the benefit of the SWF and MSCKF would have been more apparent in these cases.

@@

>>>>

\subsection{KITTI Dataset}
In addition to the ``Starry Night'' datasets, we also compared the performance of the MSCKF and SWF over four traverses from the KITTI dataset \cite{Geiger:2013:IJRR} totaling $534$ m of urban driving.
We selected these particular traverses because they contained few moving objects, which we found to be common failure cases for both filters.
To accommodate our alternative state parametrization, we used the pre-integrated linear velocity measurements provided in the dataset instead of the raw linear accelerations from the IMU. 
We extracted between 50 and 100 salient point features from the left camera in the stereo pair using Speeded Up Robust Features (SURF) \cite{Bay:2008:CVIU} and tracked them temporally using Kanade-Lucas-Tomasi (KLT) tracking \cite{Tomasi:91}.
We rejected outliers using an M-estimator Sample Consensus (MSAC) \cite{TorrZisserman:1998} procedure with a 2-point similarity transform.
% Like the ``Starry Night'' datasets, we initialized 3D points in both filters using the inverse-depth batch optimization of Section \ref{sec:featPosinvDepth}.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \vspace{-0.1cm}
\section{Conclusions} \label{sec:conclusions}
% Our results show that both the MSCKF and SWF provide substantial gains in accuracy over pure IMU integration on typical datasets with many visible features.
On the datasets we tested, the SWF slightly outperformed the MSCKF, but the MSCKF improved in accuracy with additional features while the SWF was less sensitive to feature quantity.
In relatively featureless environments, neither filter performed substantially better than pure IMU integration.

We stress that our inertial data was obtained from high-quality IMUs and has been sanitized to account for gravity, biases, and integration error.
Using a consumer-grade IMU, we expect that pure IMU integration would have performed much worse, and that the benefit of the SWF and MSCKF would have been more apparent in these cases.

@@

In future work we would like to investigate the sensitivity of these algorithms to variations in other parameters such as scene geometry, frame rate, field of view, and camera type (e.g., stereo and omnidirectional cameras).
